Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
3
push

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019. Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.  The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark. The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with lowest average square meter price valuations. A tendency visualized in the figure, is that average square meter price valuations are higher in in highly populated municipalities and in suburban areas surrounding Copenhagen. \newline

The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 million. DKK. This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models. Our research questions is as follows: 
\begin{center}
 \textit{Which features are most relevant for predicting evaluations of real estate properties in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model. Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model. As a result, a preferable machine learning model is chosen with a discussion of its usability.

@@

Within data social science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
\paragraph{On big data \& machine learning\newline}
Historically, big data has been a term reserved for data that was unable to be processed by extant software. However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data}. Annual Review of Sociology}. Today, big data is no longer too cumbersome to analyse. Matthew Salganik\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data. Salganik's tentative definition suggests that big data is not as single entity, but includes many different types of systems. Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated. Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing. It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system. This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline

@@

The technical and theoretical challenges faced by big data and machine learning research are important to consider, when employing the tools they provide. One of the major discussions revolve around machine learning's predictive capabilities. Chris Anderson\footnote{Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}} (2008) argues that since the computing power and the scale of data has increased exponentially, our reliance of scientific models could become obsolete. Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
However, many social data scientists argue against this point of view. Justin Grimmer\footnote{Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}} claims, that correlations extracted from big data cannot stand alone. Large quantities of data is not sufficient to make scientifically valid causal inferences. It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates. Indeed social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline

@@

In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data. Drawing upon the European Comissions\footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}} ethical guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered. As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} p.303} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see appendix XX)}. Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.

@@

Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real-estate sales in Denmark and has access to unique features such as "liggetid", price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}. Giving us unique insights into the pricing of real-estate in all 98 municipalities of Denmark. At the time of scraping 65,950 properties were for sale.\newline
The scraping process was conducted on Friday the 23rd of August 2019. We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}. Global Investigative Journalism Network.}. In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga. On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline
For each URL, 34 features and the target variable (price) was collected. Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

@@

Categorical: & ForClosure, Type, Municipality, lotSize	, price, rooms, size  \\	

@@

\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga. It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest. The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.

@@

\paragraph{Social and economic factors\newline}
Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors include income, reported crime, level of highest completed education etc. These are transformed into ratios, by taking the total population in a given municipality into account.   

@@

\small {All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}. 

@@

\subsection{Log Analysis}

@@

\subsection{Data Cleaning}
The scraping of Boliga left us with 65,950 observations. However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018). In the following sections we describe our data cleaning efforts. 
\subsubsection{Initial clean-up}
The initial clean-up sorted out rows that contained an illogical value. Here we focused our efforts on the removing any and all observations that contained a municipality code of 0. Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder. We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
Boliga subdivides its listings into ten real-estate types. We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model. Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand. We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that. This results in the omission of approximately 5\% of our dataset. The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean. Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
In figure XX the number of rows dropped at each step of the cleaning can be perused.
\begin{center}
\begin{tabular}{|l|c|}
\hline 
Feature & \emph{n} \\
\hline 
Municipality code & 231 \\ 
\hline 
Price & 11 \\ 
\hline 
Coordinates & 275 \\ 
\hline 
Type & 17 \\ 
\hline 
Liggetid & 3,940\\
\hline 
Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
\hline
\end{tabular} 
\end{center}

@@

The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
\begin{table}[H]
\begin{center}
\caption{Prediction Errors. \label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
  Elastic net 2-deg & 1 & 1 & 1  \\ 
  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
  Elastic Net 3-deg & 1 & 1 & 1  \\
  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
\end{tabular}
\end{center}
\end{table}
Since our efforts are aimed at predicting the valuation of a given real-estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE). Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.

@@

\newpage
\section{Appendixs}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\end{document}

>>>>

\tableofcontents
\newpage
\section{Introduction}
This report depicts a research performed regarding active Danish real estate property valuations. Since 2011, the annual number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}. The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}. Although this generally depicts a willingness of buyers to pay more for real estate property, and higher valuations from realtors, a closer analysis of active valuations adds a local view of which conditions contribute to the valuation of a real estate property. \newline
\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
\centering
\caption{}
\includegraphics[scale=0.4]{123.png}
\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
\end{figure}

Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark. The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with the lowest average square meter price valuations. A tendency visualized in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen. \newline

The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk. The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK. 15,000 to DKK. 85 million. This research paper intends to analyze real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models. Our research question is as follows: 
\begin{center}
 \textit{Which features are most relevant for predicting valuations of real estate properties in Denmark?}
\end{center}
This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset. Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model. As a result, the best performing model is chosen with a discussion of its usability.

@@

Within social data science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
\paragraph{On Big Data \& Machine Learning\newline}
Historically, big data has been a term reserved for data that was unable to be processed by extant software. However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data}. Annual Review of Sociology}. Today, big data is no longer too cumbersome to analyse. Matthew Salganik\footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data. Salganik's tentative definition suggests that big data is not a single entity, but includes many different types of systems. Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated. Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing. It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system. This algorithmic confounding force the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline

@@

The technical and theoretical challenges faced by big data and machine learning research are important to consider, when employing the tools they provide. One of the major discussions revolve around machine learning's predictive capabilities. Chris Anderson\footnote{Anderson, Chris. (2008), \textit{The end of theory: The data deluge makes the scientific method obsolete}} argues that since the computing power and the scale of data has increased exponentially, our reliance on scientific models could become obsolete. Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
However, many social data scientists argue against this point of view. Justin Grimmer\footnote{Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}} claims, that correlations extracted from big data cannot stand alone. Large quantities of data is not sufficient to make scientifically valid causal inferences. It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates. Indeed the social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline

@@

In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data. Drawing upon the European Comissions\footnote{European Commission (2018). \textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered. As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science. However, as in this instance, informed consent can be logistically impossible to collect from all participants in the study. Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}. Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center. In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests. Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}. In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function. This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see Jupyter XX)}. 

@@

Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real estate sales in Denmark and has access to unique features such as days-for-sale, price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}. Giving us unique insights into the pricing of real estate in all 98 municipalities of Denmark. 65,950 properties were for sale at the time of scraping.\newline
The scraping process was conducted on Friday the $23^{rd}$ of August 2019. Global Investigative Journalism Network.}. In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga. On the basis of these insights we constructed a code, which was able to scrape every page, containing information pertaining the currently listed real estates on Boliga. The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests. \newline
For each listed property, 34 features and the target variable (price) was collected. Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage. There are three reasons for a feature to be dropped:\newline

@@

11 features are considered to be of interest.

@@

Categorical: & ForClosure, Type, Municipality, lotSize	 \\	

@@

\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   
The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga. The function returned 65,950 URL responses, from which relevant information was extracted.\newline
As Jupyter performs poorly when running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.

@@

\paragraph{Socioeconomic Factors\newline}
Socioeconomic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. The factors include income, reported crime, level of highest completed education etc. These are transformed into ratios, by taking the total population in a given municipality into account.   

@@

\footnotesize{\textit{All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}}. 

@@

\subsection{Analysis of Scraping Logs}
Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk. This section will analyze the logs created in the scraping process, with the intention of providing evidence of the data quality. The analysis the scraping logs was done according to Snorres demand on analyzing logs. 
\paragraph{Response Code}
When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request. \textcolor{red}{Fig XA} displays response codes for the duration of the web scrapings. Every single request received a response code 200. Further evaluation of the response codes was not necessary.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{1log.png} 
  \label{fig:}
\end{figure}

\paragraph{Error Codes}
\textcolor{red}{Figure XB} plots errors codes received throughout the duration of the scrapings. Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors. The error code returns the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{2log.png} 
  \label{fig:}
\end{figure}
To understand the errors, a closer manual analysis of the log was performed on requests receiving errors. The errors occur in random intervals and are subsequently followed by another request to an identical URL. Therefore, we assessed that these errors were due to connection problems or server traffic. Since the errors were corrected by a following request, we assessed it would not affect the research.

\paragraph{Server Response Times}
An indicator of poor data quality is varying the response times from the server being scraped. \textcolor{red}{Figure XC} plots changes in response times for the duration of the web scrapings. The 3 data sources all resulted in few variations of response times.  Responses times differing from usual within the logs, have been assessed to be caused by two either a slow server time or connection, or due to larger quantities of data being requested. To validate the quality of data, manual control of the returned result and the webpage result was performed, without the notice of significant corruptions in the data to be utilized in the research.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{3log.png} 
  \label{fig:}
\end{figure}

\paragraph{Response Sizes}
To validate the response quality, an assessment of the response size was performed. \textcolor{red}{Figure XD} plots response sizes throughout the duration of the web scrapings. Boliga contains a single noticeable large response size within short time, while hvorlangterder response sizes vary throughout the scrape. The DAWA scrape resulted in indifferent response sizes, and therefore needed no further investigation. 
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{4log.png} 
  \label{fig:}
\end{figure}
With a further analysis the distribution of sample sizes in figure XE, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log. By manually assessing the returned output of the Boliga scrape, these two requests were found to return a larger amount of data than usual. The two requests were made to two pages, where few properties contain nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column. These dictionaries are image descriptions, and are not utilized within this research. These larger responses were deemed as not polluting the results of the research.
\begin{figure}[H]
  \centering
   \caption{}
   \includegraphics[width=\linewidth]{5log.png} 
  \label{fig:}
\end{figure}
\textcolor{red}{Figure XE depicts that the hvorlangerder response sizes are a bit left scewed, while Figure XD} shows that the distribution of large sizes happens during the middle of the scrape. With a further glimpse into the log, we observed two things. First, all response sizes of 0 are related to the errors, displayed in figure XB. The variance of responses could be explained by the type of data retrieved from the scrape. The request was set to return names, addresses, distances and other information, which sizes are varying in nature. When extracting the value from every single key of the dictionary output, no errors or missing values were found. Further control of samples of large and small sizes were performed without discovering flaws. The response sizes from hvorlangterder are found to vary by nature, which may explain the difference.

\paragraph{Assesment of the Scraping Logs}
The individual analyses of the scraping logs showed minor suspicious traits which were assessed manually through the output or logs. The most concerning analysis being difference in response sizes and response times from the hvorlangterder scrape. This scrape consumed large amounts of time and computing power, as every single observation from the Boliga data, had to be input for requesting a response. In an extensive research, these problems could be handled by gaining direct access to the website instead of scraping and would benefit by running on a server with greater computing power. The results of the data collection were evaluated to be satisfying, and not corrupting the results of our research, as fairly reasonable explanations for noticeable dissimilarities within the logs were found.

\paragraph{Critique of Logs Using Scraping Class}
In the process of analyzing the scraping logs, minor flaws from the scraping library named ‘scraping\_class’ were detected. The returned columns ‘t’ and ‘delta\_t’ contained non-generic formats of epoch time. This was fixed by applying string manipulation and datetime conversions.

@@

\subsection{Data Cleaning}
The scraping of Boliga left us with 65,950 observations. However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018). In the following sections we describe our data cleaning efforts. 
\subsubsection{Initial clean-up}
The initial clean-up sorted out rows that contained an illogical value. Here we focused our efforts on the removing any and all observations that contained a municipality code of 0. Additionally, we chose to exclude any real estate valued below DKK. 100, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder. We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
Boliga subdivides its listings into ten real estate types. We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model. Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
We dropped all observations with an unreasonably high days-for-sale, as we saw these instances to not  represent reasonable pricing or demand. We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that. This results in the omission of approximately 5\% of our dataset. The highest mean "days-for-sale" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean. Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
In figure XX the number of rows dropped at each step of the cleaning can be perused.
\begin{center}
\begin{tabular}{|l|c|}
\hline 
Feature & \emph{n} \\
\hline 
Municipality code & 231 \\ 
\hline 
Price & 11 \\ 
\hline 
Coordinates & 275 \\ 
\hline 
Type & 17 \\ 
\hline 
days-for-sale & 3,940\\
\hline 
Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
\hline
\end{tabular} 
\end{center}

@@

The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
\begin{table}[H]
\begin{center}
\caption{Prediction Errors. \label{time}}
\begin{tabular}{| c | c | c | c | c | c |} 
\hline
   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
  Elastic net 2-deg & 1 & 1 & 1  \\ 
  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
  Elastic Net 3-deg & 1 & 1 & 1  \\
  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
\end{tabular}
\end{center}
\end{table}
Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE). Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.

@@

\newpage
\section{Appendix}
\subsubsection{}
Excluded Features:\newline
municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
\subsubsection{}
The model used for prediction: 
$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
$$\textbf{X}_j=\begin{bmatrix}
           basementSize \\
           buildYear \\
           rooms \\
           size \\
           primary\_school\_educ \\
           high\_school\_educ \\
           vocational\_educ \\
           SHE \\
           MHE \\
           bachelors\_degree \\
           LHE \\
           avg\_municipal\_income\_2017 \\
           Population\_in\_urban\_development \\
           Socioeconomic\_index \\
           lake\_distance\\
           doctor\_distance \\
           supermarket\_distance \\
           school\_distance \\
           daycare\_distance \\
           hospital\_distance \\
           train\_distance \\
           pharmacy\_distance \\
           library\_distance \\
         \end{bmatrix}$$
\end{document}
